This internship is compulsory and carried out at the end of the fourth year. During this internship, the student has to put into practice the knowledge acquired during his training and should improve his skills whithin the company. At the end of the intership, the student must write a report. The internship's validation depends on the quality of the work, the report and the evaluation sheet of the industrial tutor.\\
This internship took place at Data Publica, an open data pioneer in France. Data Publica is a young start-up (founded in July 2011) specialized in business data, open data, big data and DataViz. Data Publica employs fourteen dynamic and competent people. Data Publica is developing C-Radar, a predictive selling product built on French companies informations, like administrative, financial, web, social networks and media. C-Radar is made of big data technologies (crawling, scraping or machine learning).\\
My mission at Data Publica, was to build an automatic processing chain, a Python plugin, to which you give a list of textual records as an input. In return, you get a list of tagged documents according to their subject interest (job offer, event participation, staff nomination, fundraising, etc).\\
The directed tasks linked to the detection of information in the records are Text Mining and Natural Language Processing (also Information Retrieval). Skills in Machine Learning are also required.\\
My internship missions were all completed, the Python plugin is running and able to classify records.